R Notebook

### 2023-01-05 Code/Simulation.Rmd
Corrected naive case

# Test non-parametric bootstrap as a solution to fitted parameters
test_autoarma <- function(x, pdist, qdist, B, working) {
  p.value <- ks.arma(x = x, pdist = pdist, qdist = qdist, B = 1000, working = working)
  counter <<- counter + 1
  cat(counter, "")
  list(p.value = p.value)
}

# Naive function that incorrectly uses fitted parameters for gamma distribution
test_super_naive_autoarma <- function(x) {

# Generate results
n_tests = 1000
n = 200
phi <- .3
theta <- .2
qdist <- function(u) qgamma(u, shape = 3, scale = 1)
pdist <- function(u) pgamma(u, shape = 3, scale = 1)
working <- "auto"
counter <- 0
pvals_autoarma <- replicate(n_tests, test_autoarma(x = genData(n, phi, theta, qdist), pdist = pdist, qdist = qdist, B = 1000, working = working)$p.value)
counter <- 0
pvals_naive <- replicate(n_tests, test_super_naive_autoarma(genData(n, phi, theta, qdist))$p.value)

>>>>

# Test autoarma as a solution to correlated data
test_autoarma <- function(x, pdist, qdist, B, working) {
  p.value <- ks.arma(x = x, pdist = pdist, qdist = qdist, B = 1000, working = working)
  counter <<- counter + 1
  cat(counter, "")
  list(p.value = p.value)
}

# Generate results
nrep <- 1000
n <- 200
phi <- .3
theta <- .2
shape <- 3
scale <- 1
qdist <- function(u) qgamma(u, shape = shape, scale = scale)
pdist <- function(u) pgamma(u, shape = shape, scale = scale)
working <- "auto"
counter <- 0
pvals_autoarma <- replicate(nrep, test_autoarma(x = genData(n, phi, theta, qdist), pdist = pdist, qdist = qdist, B = 1000, working = working)$p.value)
counter <- 0
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, phi, theta, qdist),
                                                   pdist = pgamma,
                                                   shape = shape, 
                                                   scale = scale)$p.value)
